Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-01 paper/paper.tex
intro edits

While the general idea of measuring a Doppler shift by the relative motions of stellar absorption lines is fairly straightforward, there are considerable subtleties to implementing this, from the choice of template

We begin in Section \ref{s:methods} with a summary of the practices used by current \RV\ pipelines, including cross-correlation and template fitting. We then implement these techniques to extract \RV s from a 5-\r{A} section of simulated spectrum and compare their performance in Section \ref{s:fakedata}.

@@

The assumption of this project is that we have many observations of the same star with good coverage throughout the observing season, so that we have seen the star many times spanning the range of telluric-to-star relative RV shifts. This means we are not considering the case of a real-time data reduction pipeline. We also assume a HARPS-like setup, i.e. no absorption cell, but the points we make can be easily generalized to the gas-cell case. We return to this point in the discussion \todo{(do this)}.

@@

@@

\section{Data}

@@

\section{Experiments}

@@

\section{Summary \& Discussion}

@@

\acknowledgements
MPIA hospitality, Montet, Foreman-Mackey, Bean, Sturmer, Rix, HARPS team, ESO, Stars group meeting, Brewer

>>>>

While the general idea of measuring a Doppler shift by the relative motions of stellar absorption lines is fairly straightforward, there are considerable subtleties to implementing this, from the choice of reference spectrum or template to the treatment of telluric absorption features. Ultra-stabilized spectrographs like HARPS \todo{(define \& cite)} predominantly utilize a cross-correlation method with a custom-built list of spectral lines (see e.g. ...).

@@

We begin in Section \ref{s:info} with a derivation of the information-theory-based limit on the RV information content of a spectrum. In Section \ref{s:methods}, we summarize common RV extraction practices used by current \RV\ pipelines, including cross-correlation and template fitting. We then implement these techniques to extract \RV s using 5-\r{A} section of simulated and real spectra, as described in Section {s:data}. We compare the relative performances of the methods in Section \ref{s:experiments} and conclude with some recommendations for future RV pipelines in Section {s:summary}.

It is important to state at the outset the assumptions under which are operating for these experiments. We assume that our data set consists of multiple observations of the same star with good coverage throughout the observing season, so that we have seen the star many times spanning the range of telluric-to-star relative RV shifts. This means we are not considering the case of a real-time data reduction pipeline. We also assume a HARPS-like setup, i.e. no absorption cell, but the points we make can be easily generalized to the gas-cell case. We return to this point in the discussion \todo{(do this)}.

@@

[any other assumptions?]

@@

\section{Data}
\label{s:data}

@@

\section{Experiments}
\label{s:experiments}

@@

\section{Summary \& Discussion}
\section{s:summary}

@@

\acknowledgements
MPIA hospitality, Montet, Foreman-Mackey, Bean, Stuermer, Rix, HARPS team, ESO, Stars group meeting, Brewer
